Identifying Drawings with the Quick Draw Challenge

### 2018-12-06 report/report_draft.Rmd
minor suggestions on report format

$H_a:$ Prediction will go up when we use a CNN compared to a fully
	connected feedforward neural network.

$H_a:$ Prediction will go up when we use regularization.

$H_a:$ Run neural networks without any activations.

$H_a:$ Try different architectures- number of layers, different (or no) 
activations

$H_a:$ CNN with dilation is preferable to LSTM because it's presumably
faster. We can cite some papers here.

@@

>>>>

$H1_a:$ Prediction will go up when we use a CNN compared to a fully
	connected feedforward neural network.

$H2_a:$ Prediction will go up when we use regularization.

$H3_a:$ Run neural networks without any activations.

$H4_a:$ Try different architectures- number of layers, different (or no) 
activations

$H5_a:$ CNN with dilation is preferable to LSTM because it's presumably
faster. We can cite some papers here.

@@

| Hypothesis | Result         |
| ---------- | -------------- |
| $H1_a$     | Accept         |
| $H2_a$     | Fail to Accept |
| $H3_a$     | Fail to Accept |
| $H4_a$     | Accept         |
| $H5_a$     | Fail to Accept |

## Fully Connected Neural Network

Here's the run down on it and how it relates
to the hypotheses.

## Convolutional Neural Network

same thing for the CNN. TOOD: can we fold in some of
the specializations into this section??

### 2018-12-06 report/report_draft.tex
minor suggestions on report format

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Identifying Drawings with the Quick Draw Challenge},
            pdfauthor={Group 3},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\section{Introduction}\label{introduction}

@@

\section{Methods}\label{methods}

@@

\subsubsection{EDA}\label{eda}

@@

\(H_a:\) Prediction will go up when we use a CNN compared to a fully
connected feedforward neural network.

\(H_a:\) Prediction will go up when we use regularization.

\(H_a:\) Run neural networks without any activations.

\(H_a:\) Try different architectures- number of layers, different (or
no) activations

\(H_a:\) CNN with dilation is preferable to LSTM because it's presumably
faster. We can cite some papers here.

@@

\section{Results}\label{results}

@@

\section{Discussion}\label{discussion}

@@

\section{References}\label{references}

\section{Appendix}\label{appendix}

@@

\section*{Statement of contribution}\label{statement-of-contribution}
\addcontentsline{toc}{section}{Statement of contribution}

\hypertarget{refs}{}
\hypertarget{ref-QuickDra10}{}
Google. 2018. ``Quick, Draw! Doodle Recognition Challenge \textbar{}
Kaggle.'' \url{https://www.kaggle.com/c/quickdraw-doodle-recognition}.

>>>>

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Identifying Drawings with the Quick Draw Challenge},
            pdfauthor={Group 3},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{methods}{%
\section{Methods}\label{methods}}

@@

\hypertarget{eda}{%
\subsubsection{EDA}\label{eda}}

@@

\(H1_a:\) Prediction will go up when we use a CNN compared to a fully
connected feedforward neural network.

\(H2_a:\) Prediction will go up when we use regularization.

\(H3_a:\) Run neural networks without any activations.

\(H4_a:\) Try different architectures- number of layers, different (or
no) activations

\(H5_a:\) CNN with dilation is preferable to LSTM because it's
presumably faster. We can cite some papers here.

@@

\hypertarget{results}{%
\section{Results}\label{results}}

@@

\begin{longtable}[]{@{}ll@{}}
\toprule
Hypothesis & Result\tabularnewline
\midrule
\endhead
\(H1_a\) & Accept\tabularnewline
\(H2_a\) & Fail to Accept\tabularnewline
\(H3_a\) & Fail to Accept\tabularnewline
\(H4_a\) & Accept\tabularnewline
\(H5_a\) & Fail to Accept\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{fully-connected-neural-network}{%
\subsection{Fully Connected Neural
Network}\label{fully-connected-neural-network}}

Here's the run down on it and how it relates to the hypotheses.

\hypertarget{convolutional-neural-network}{%
\subsection{Convolutional Neural
Network}\label{convolutional-neural-network}}

same thing for the CNN. TOOD: can we fold in some of the specializations
into this section??

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

@@

The model built using CNN was better than human accuracy, which was in
turn better than the model built using fully connected network.

\hypertarget{references}{%
\section{References}\label{references}}

\hypertarget{appendix}{%
\section{Appendix}\label{appendix}}

@@

\hypertarget{statement-of-contribution}{%
\section{Statement of contribution}\label{statement-of-contribution}}

Everyone worked on everything.

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-QuickDra10}{}%
Google. 2018. ``Quick, Draw! Doodle Recognition Challenge \textbar{}
Kaggle.'' \url{https://www.kaggle.com/c/quickdraw-doodle-recognition}.
